---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# aaegdata

This is a data package containing Aedes aegypti vector mosquitoes biological relevant molecular and biochemical data. Data colected from public available databases and presented here in a clean, structured and ready to use format. The consistent format used for the data allows the use of modern syntax and tools to be used with this package. 

## Installation

<!-- You can install the released version of aaegdata from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("aaegdata")
```
-->
 You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("luciorq/aaegdata")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

----
Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
